Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-12-15 Manuscript/Manuscript.Rmd

# packages
library(tidyverse)
library(mice)
library(miceadds)
library(metamisc)
library(pan)

@@

Toy example from [Heckman Github repo](https://github.com/johamunoz/Heckman-IPDMA/blob/main/Toy_example.R).

>>>>

# packages
library(tidyverse)
library(mice)
library(miceadds)
library(metamisc)
library(GJRM)
library(pan)

@@

Toy example from [Heckman Github repo](https://github.com/johamunoz/Heckman-IPDMA/blob/main/Toy_example.R). We will use the following variables:

  - `region` Cluster variable,
  - `hiv` HIV diagnosis (0=no, 1=yes),
  - `age` Age of the patient,
  - `marital` Marital status,
  - `condom` Condom use during last intercourse,
  - `smoke` Smoker (levels).

```{r hiv, echo=FALSE}
# data
data("hiv")
hiv <- hiv %>% 
  select(c("region","hiv", "age", "marital", "condom", "smoke")) %>% 
  mutate(region = as.integer(region))
# md pattern
plot_md_pat(hiv)
```
